Moving Towards Reproducible and Programmatic Generation of Neuroimaging Visualizations

### 2022-09-04 SupplementA_R_Figs.Rmd
svg check

```{r Fig1 compile, eval=FALSE}
# This code block complies all the panels of the figure into one, largely using the patchwork package.

@@

fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g1', 'fig1g2', 'fig1g3','fig1h', 'fig1i')
figs <- list()

patchwork <- figs[[1]]/figs[[2]]|((figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]]) + 
  plot_layout(heights = c(0.8,0.8,1.5))|((figs[[3]]/figs[[4]]/figs[[10]]) + 
                                           plot_layout(heights = c(0.5,1,1)))

patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations made in R') &
  theme(plot.tag = element_text(face = 'bold'),
        plot.title = element_text(face="bold"))

>>>>

```{r Fig1 compile, eval=FALSE}
library(patchwork)
library(ggplot2)

fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g', 'fig1h', 'fig1i')
figs <- list()

patchwork <- figs[[1]]/figs[[2]]|((figs[[3]]/(figs[[4]]|figs[[5]]))/figs[[6]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[7]]/figs[[8]]/figs[[9]])+plot_layout(heights = c(0.5,1,1)))

svg("data/R/Figure1.svg")
patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations made in R') &
  theme(plot.tag = element_text(face = 'bold'),
        plot.title = element_text(face="bold"))
dev.off()

```{r Figure2, eval=FALSE}

@@

fig_name <- c('fig2a', 'fig2b', 'fig2c', 'fig2d', 'fig2e', 'fig2f')
figs <- list()

for (f in 1:length(fig_name)) { 
  knitr::plot_crop(paste0('data/python/',fig_name[f],'.png'))
  figs[[f]] <- ggplot() +
    annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/python/',fig_name[f],'.png')),
                                       width=ggplot2::unit(1,"npc"),
                                       height=ggplot2::unit(1,"npc")))
}

layoutA <- "
AAAA
#BB#
CCCC
"
patchworkABC <- ((figs[[1]] + figs[[3]] + plot_layout(widths  = c(0.6,1))) / figs[[2]])  + plot_layout(heights = c(1,0.5))

patchworkDEF <-  (figs[[4]] / figs[[5]] / figs[[6]] + plot_layout(design = layoutA, widths = c(0.2,1,0.2)))

patchwork <- (patchworkABC| patchworkDEF)  + plot_layout(widths = c(1,0.6))

#svg("data/R/Figure2.svg")
patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations made in Python') &
  theme(plot.tag = element_text(face = 'bold'),
        plot.title = element_text(face="bold"))
#dev.off()

### 2022-09-04 manuscript.Rmd
svg check

library(patchwork)
library(ggplot2)

fig_name <- c('fig1a', 'fig1b', 'fig1c', 'fig1d', 'fig1e', 'fig1f', 'fig1g', 'fig1h', 'fig1i')
figs <- list()

for (f in 1:length(fig_name)) { 
  knitr::plot_crop(paste0('data/R/',fig_name[f],'.png'))
  figs[[f]] <- ggplot() + annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/R/',fig_name[f],'.png')),
                                                             width=ggplot2::unit(1,"npc"),
                                                             height=ggplot2::unit(1,"npc")))
}

patchwork <- figs[[1]]/figs[[2]]|((figs[[3]]/(figs[[4]]|figs[[5]]))/figs[[6]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[7]]/figs[[8]]/figs[[9]])+plot_layout(heights = c(0.5,1,1)))

patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations made in R') &
  theme(plot.tag = element_text(face = 'bold'),
        plot.title = element_text(face="bold"))

@@

library(patchwork)
library(ggplot2)

fig_name <- c('fig2a', 'fig2b', 'fig2c', 'fig2d', 'fig2e', 'fig2f')
figs <- list()

for (f in 1:length(fig_name)) { 
  knitr::plot_crop(paste0('data/python/',fig_name[f],'.png'))
  figs[[f]] <- ggplot() +
    annotation_custom(grid::rasterGrob(png::readPNG(paste0('data/python/',fig_name[f],'.png')),
                                       width=ggplot2::unit(1,"npc"),
                                       height=ggplot2::unit(1,"npc")))
}

layoutA <- "
AAAA
#BB#
CCCC
"
patchwork1 <- (((figs[[1]] + figs[[3]]) + plot_layout(widths  = c(0.8,1))) / figs[[2]])  + plot_layout(heights = c(1,0.5)) 
patchwork1

patchwork2 <-  (figs[[4]] / figs[[5]] / figs[[6]]) + plot_layout(design = layoutA, widths = c(0.2,1,0.2))

(patchwork1 | patchwork2) + plot_layout(widths = c(1,0.6))

patchwork2 <-  (figs[[4]] / figs[[5]] / figs[[6]] + plot_layout(design = layoutA, widths = c(0.2,1,0.2)))

patchwork2

patchwork + plot_annotation(tag_levels = 'A',
                            title = 'Examples of brain visualizations made in Python') &
  theme(plot.tag = element_text(face = 'bold'),
        plot.title = element_text(face="bold"))

>>>>

knitr::include_graphics("data/R/Figure1.svg")

@@

knitr::include_graphics("data/python/Figure2.pdf")
